pdp: An R Package for Creating Partial Dependence Plots

### 2016-09-07 manuscript/greenwell.tex
fixed typo

library(ggplot2)
ggplot(pd, aes(x = Petal.Width, y = Petal.Length, z = y, fill = y)) +
  geom_tile() + 
  geom_contour(color = "white", alpha = 0.5) + 
  scale_fill_distiller(palette = "Spectral", na.value = "white") + 
  theme_bw() +
  facet_grid(~ Species)
\end{example}

>>>>

library(ggplot2)
ggplot(pd, aes(x = Petal.Width, y = Petal.Length, z = y, fill = y)) +
  geom_tile() + 
  geom_contour(color = "white", alpha = 0.5) + 
  scale_fill_distiller(palette = "Spectral") + 
  theme_bw() +
  facet_grid(~ Species)
\end{example}
